% Martin Rodriguez Jr.
% SID: 811958765


%Anything following a % sign is a comment.
%Please use the comments to help you understand the code below.

%%%%%%%%%%%% Quick Notes %%%%%%%%%%%%%%%%%%%%%%

% \textit{} ==> italicises words or phrases
% \textbf{} ==> bolds words or phrases
% \\ ==> creates a new line
% \S ==> creates section section symbol, fancy double s thing
% \renewcommand{\baselinest8retch}{2} ==> double spaces the document

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt]{article}

%LOAD VARIOUS PACKAGES
\usepackage{setspace}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphics, latexsym, multicol}		%
\usepackage{graphicx}
\usepackage{lscape}

\usepackage{amsmath, amsfonts, amsthm, amssymb}		%Math packages provided by American Math Society (AMS)
\usepackage{thmtools}

\usepackage{xcolor}							%Extended color package: provides colors for text enhancement
%\usepackage[margin = 1.00in, top = 1in, bottom = 1in, nohead] {geometry}
\usepackage{boxedminipage}					%allows use of boxed minipages
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

\usepackage[english]{babel}
\usepackage{xcolor} % Required for specifying custom colors
\usepackage{ulem}
\usepackage{fix-cm}
% \usepackage[ruled,vlined]{algorithm2e}
\usepackage{algorithm, algorithmic}
% Include macros file
\input{macros.tex}

\title{MOOD limiting for high-order discontinuous Galerkin methods}
\date{\today}
\author{Martin Rodriguez ~~~ Dongwook Lee \\ {\small Department of Applied Mathematics,  University of California, Santa Cruz} \\[11pt] Will Pazner \\ {\small Center for Applied Scientific Computing, Lawrence Livermore National Laboratory} }

\usepackage{setspace}

\begin{document}
\maketitle

\onehalfspacing

\section{Introduction}


One of the current issues with high-order discontinuous Galerkin (DG) methods arises at discontinuities in the solution. The discontinuities cause unwanted oscillations and need to be dampened through classic limiting methods used finite volume (FV) methods or aritificial diffusion. Limiting methods tend to drop to first order accurate and disregard high-order accurate information. 

When trying to find a stable solution there are two steps we need to take: 
\begin{enumerate}[label=\roman*]
    \item Identify a troubled cell, and
    \item compute a limited solution.
\end{enumerate}
In \cite{qiu2005comparison} they present a comparison of different troubled cells indicators and are paired with a WENO limiter. In \cite{persson2006sub,pazner2021sparse} use a smoothness indicator denoted by
\begin{align}
    s_{K} = \log_{10}\left( \frac{ \| \boldu_K - \hat{\boldu}_K\|^2_2 }{ \| \boldu_K \|^2_2 } \right),
\end{align}
where $\boldu_K$ is the nodal solution in element $K$, and $\hat{\boldu}_K$ is a truncated modal solution in element $K$. Then based on $s_{K}$, a smoothing factor, $\varepsilon_K$, can be computed. Another indicator is presented in \cite{ray2018artificial}, where they present an artificial neural network to find troubled cells.

Biswas et al. \cite{biswas1994parallel} present a way to systematically cascade through the modes of the solution and \cite{krivodonova2007limiters} presents an updated version of the method. Another similar approach is to use multi-dimensional optimal order detection (MOOD) which is used to cascade through the desired polynomial orders. This method was first introduced in \cite{clainavery} and improved in \cite{diot2012improved}. Dumbser et al. \cite{dumbser2014posteriori} have introduced a subcell MOOD limiting method that uses the element nodes as cell-centered values and use a WENO reconstuction to obtain a high-order method.  

Recently, \cite{bourgeois2021gp} used a GP-MOOD method for posteriori limiting on a small amount of cells. The GP-MOOD method uses a series of criteria to identify troubled cells and use a GP reconstruction to compute a lower order method before reducing to a first order Godunov method. We plan on adopting the criteria check to identify troubled cells and then cascade through the modes of the solution until we identify an acceptable solution or reaching a constant (zeroth order polynomial) solution. 

\section{Basic Methodology}
In this methodology we will use troubled cell indicators developed in \cite{bourgeois2021gp} and use a truncation of modal solutions as the limiting method. 

The criteria are as follows:
\begin{enumerate}[label=(\alph*)]
    \item Physical admissibility detection (PAD): this criteria is to ensure positivity on density and pressure variables.
    \item Computer science admissibility detection (CAD): criteria to identify whether density or pressure are \texttt{NaN} or \texttt{inf}.
    \item Compressibility-Shock detection (CSD): this detector measures the compressibility and the shock strength of the element. We check the following numerical quantities:
    \begin{align}
        \nabla \cdot \bar{V} \geq -\sigma_v, ~~~ \tilde{\nabla}\bar{p} \leq \sigma_p,
    \end{align}
    where $\sigma_v$ and $\sigma_p$ are both tunable parameters.
    \item Relaxed DMP criteria: plateau + DMP + u2
\end{enumerate}

% \begin{enumerate}
%     \item Compute unlimited nodal solution $\boldu$ and modal solution $\hat{\boldu} = V^{-1} \boldu$, $V$ is the Legendre polynomial Vandermonde matrix.
%     \item Compute cell-center averages $\bar{\boldu}$.
%     \item Perform the PAD and CAD criteria check as in \cite{bourgeois2021gp}.
%     \begin{enumerate}
%         \item If it does not pass then truncate the current highest mode in the solution and reperform check. 
%     \end{enumerate}
%     \item Perform the strong compressibility and shocks check as in \cite{bourgeois2021gp}.
%     \begin{enumerate}
%         \item If present, then does it meet the DMP criteria? Truncate highest mode in modal solution and reperform all criteria checks.
%     \end{enumerate}
%     \item If it meets the criteria above then we accept the truncated modal solution and recompute the nodal solution $\boldu = V\hat{\boldu}$.
% \end{enumerate}



\bibliographystyle{plain}
\bibliography{dgm-refz.bib}


\end{document}